### 2015-05-13 corral.tex
footnote about weak memory

Our approach to accelerating \corral is simple and yet effective: we simplify
the sequentialization that \corral performs by instrumenting \texttt{yield}
statements only at shared memory accesses that \whoop reported as potentially
racy. This effectively acts as a partial-order reduction that can significantly
reduce the number of interleavings that \corral needs to explore, and thus
increase performance and scalability.

>>>>

Our approach to accelerating \corral is simple and yet effective: we simplify
the sequentialization that \corral performs by instrumenting \texttt{yield}
statements only at shared memory accesses that \whoop reported as potentially
racy.\footnote{In the presence of data races and relaxed memory, even considering all interleavings of shared memory accesses may be insufficient to find all bugs.} This effectively acts as a partial-order reduction that can significantly
reduce the number of interleavings that \corral needs to explore, and thus
increase performance and scalability.
